Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-24 doc/PRF2022/PRF_main.tex
YNY july24

\begin{abstract}
% insert abstract here
\end{abstract}

>>>>

\begin{abstract}
Active colloidal systems with non-equilibrium self-organization is a long-standing challenge in biology. To understand how hydrodynamic flow may be used
to actively control self-assembly of Janus particles (JPs),  we use a model recently developed for the many-body hydrodynamics of amphiphilic JPs suspended 
in a viscous background flow (JFM, 941, 2022). We investigate how various bilayer structures arise from tuning the hydrophobicity/hydrophilicity of the JPs. 
Focusing on three distributions of hydrophobicity we found JPs may assemble into uni-lamella, multi-lamella, and striated structures in a viscous fluid. 
Under a linear flow and a Taylor-Green mixing flow,  we use three measures to quantify the collective dynamics of JP particles under a background flow: 
(a) Free energy from the hydrophobic interactions between the JPs, (b) an order parameter for the ordering of JPs in terms of alignment of their directors, 
and (c) a strain parameter that captures the deformation in the assembly. We found the dynamics of these three measures correlate well with the hydrodynamics 
of JPs. These numerical provide insights into dynamic control of non-equilibrium active biological systems with similar self-organization.
% insert abstract here
\end{abstract}
